How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
Reorder related work, to flow better
Signed-off-by: Stefan Marr <git@stefan-marr.de>

Optimization Coaching
\citep{St-Amour:2012:OCO} is a related approach more
directly integrated into the language runtime and development environment.
Optimizer Coaching uses feedback from the runtime to guide developers
to insert or change type declarations 
to enable a compiler to generate a more optimal program.
In this spirit, we would eventually want to achieve the same, although
in our case,
we need to run full experiments to get the necessary information.
Furthermore, we still lack the seamless integration in a development environment.

The high-performance computing community has been investigating how
tools and visualization can help developers to utilize their systems
more efficiently \citep{Papenhausen:2016:IVT,daSilva:2019:PSV}.
Their focus is typically on parallelisation opportunities,
guided by runtime feedback, cost models, or heuristics. 
Their large body of work \citep{Isaacs:2014:PerfViz} uses various approaches,
though, we are not aware of work that has used an approach similar to ours.
One may argue, this is largely a question of practicality.

>>>>

The high-performance computing community has been investigating how
tools and visualisations can help developers to utilise their systems
more efficiently \citep{Papenhausen:2016:IVT,daSilva:2019:PSV}.
Their focus is typically on parallelisation opportunities,
guided by runtime feedback, cost models, or heuristics. 
Their large body of work \citep{Isaacs:2014:PerfViz} uses various approaches,
though, we are not aware of work that has used an approach similar to ours.

At the moment, our approach to identifing type annotations that case
performance anomalies is not integrated into a development environment.
Though, for instance Optimization Coaching
\citep{St-Amour:2012:OCO} is a promising direction.
Optimization Coaching uses feedback from the runtime to guide developers
to insert or change type declarations 
to enable a compiler to generate a more optimal program.
In this spirit, we would eventually want to achieve the same, although
in our case,
we need to run full experiments to get the necessary information.
